---
title: "Effects of Climate Change on Hydrologic Units in Phase 1"
author: "Daryl Van Dyke"
date: "August 31, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This report summarizes the results of initial data analysis for the climate change effects on hydrologic and climatic variable in the Phase 1 area of the terrestrial SHC project in the Klamath Basin.


```{r, hide = TRUE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(reshape2)

genSeq <- function(inputList){
                i = 1
                mybiglist <- vector('integer',1116)
             for( year in inputList){
                     #print(year)
                     j = 1
                     rep(year,12) -> tmp
                     while(j < 13){
                             mybiglist[i] <- tmp[j]
                             i = i + 1
                             j = j + 1
                     }
                     
             }
        return(mybiglist)
        }

nameFixer<- function(inputDF){
        paste(names(inputDF), ".ppt", sep = "") -> names1
        inputDF$TIMESTAMP <- inputDF$TIMESTAMP.ppt
        names(inputDF) <- names1
        }

makeMeans_mm_to_m <- function(inputDF){

        #vDates <- as.Date(inputDF$TIMESTEP.ppt)
        
        select(inputDF, contains("mean")) -> meanTemp
        tbl_df(meanTemp/1000) -> meanTemp2
        
        #now calc Areas
        zeros <- matrix(rep(0.0,16*16),nrow = 16)
        diag(zeros) <- as.matrix(vAreas)

        as.matrix(meanTemp2) %*% zeros -> tmp3

        tmpNames <- names(meanTemp)
        gsub(".m..",".m3.pptV",tmpNames) -> newNames
        #return(newNames)
        dfTmp <- tbl_df(tmp3)
        
        names(dfTmp)<- newNames
        dfTmp$Date <- as.Date(inputDF$TIMESTEP)
        #return(names(dfTmp))
        return(dfTmp)
        }

grabSID <- function(inputSID = 1003){
        C1 <- dfAccPPT_PCM$Date
        indxSID <- inputSID - 999
        C2  <- as.vector(dfAccPPT_GISS[,indxSID])
        C3  <- as.vector(dfAccPPT_CCSM[,indxSID])
        C4  <- as.vector(dfAccPPT_Miro[,indxSID])
        C5  <- as.vector(dfAccPPT_PCM[,indxSID])
        C6  <- as.vector(dfAccPPT_CNRM[,indxSID])
        names <- c("Date", "GISSpptV","CCSMpptV", "MiroPptV", "PCMpptV", "CNRMpptV")
        
        out<- cbind(C1, C2, C3, C4, C5, C6)
        names(out) <- names
        dfOut <- tbl_df(out)
        #names(dfOut) <- names
        return(dfOut)
        }

grabSIDHist <- function(inputDF, inputSID = 1003){
        C1 <- inputDF$Date
        indxSID <- inputSID - 999
        C2  <- as.vector(inputDF[,indxSID])
        names <- c("Date", "HistpptV")
        
        out<- cbind(C1, C2)
        names(out) <- names
        dfOut <- tbl_df(out)
        #names(dfOut) <- names
        return(dfOut)    
        }


```

## Analysis Set Up

```{r}
Phase1Huc10_CCSMrpc85_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/PPT/Phase1Huc10_CCSMrpc85_Ppt.csv")
Phase1Huc10_CNRMcm5rcp85_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/PPT/Phase1Huc10_CNRMcm5rcp85_Ppt.csv")
Phase1Huc10_GISS.AOM.A1B_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/PPT/Phase1Huc10_GISS-AOM-A1B_Ppt.csv")
Phase1Huc10_Miroc5Rcp26_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/PPT/Phase1Huc10_Miroc5Rcp26_Ppt.csv")
Phase1Huc10_PCM.A2_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/PPT/Phase1Huc10_PCM-A2_Ppt.csv")

# Copy to DF and Delete Temp Tables
dfGISS <- tbl_df(Phase1Huc10_GISS.AOM.A1B_Ppt)
dfCCSM <- tbl_df(Phase1Huc10_CCSMrpc85_Ppt)
dfCNRM <- tbl_df(Phase1Huc10_CNRMcm5rcp85_Ppt)
dfPCM  <- tbl_df(Phase1Huc10_PCM.A2_Ppt)
dfMiro <- tbl_df(Phase1Huc10_Miroc5Rcp26_Ppt)

rm(Phase1Huc10_PCM.A2_Ppt)
rm(Phase1Huc10_CCSMrpc85_Ppt)
rm(Phase1Huc10_Miroc5Rcp26_Ppt)
rm(Phase1Huc10_CNRMcm5rcp85_Ppt)
rm(Phase1Huc10_GISS.AOM.A1B_Ppt)

dfGISS$Date <- as.Date(dfGISS$TIMESTEP)
dfPCM$Date  <- as.Date(dfPCM$TIMESTEP)
dfMiro$Date <- as.Date(dfMiro$TIMESTEP)
dfCNRM$Date <- as.Date(dfCNRM$TIMESTEP)
dfCCSM$Date <- as.Date(dfCCSM$TIMESTEP)

dfGISS$hy[1:1116] <- genSeq(2006:2100)[1:1116] 
dfPCM$hy[1:1116]  <- genSeq(2006:2100)[1:1116] 
dfMiro$hy[1:1116] <- genSeq(2006:2100)[1:1116]
dfCNRM$hy[1:1116] <- genSeq(2006:2100)[1:1116] 
dfCCSM$hy[1:1116] <- genSeq(2006:2100)[1:1116]

dfGISS$hyf <- paste("hy",dfGISS$hy, sep = "")
dfPCM$hyf  <- paste("hy",dfPCM$hy, sep = "")
dfMiro$hyf <- paste("hy",dfMiro$hy, sep = "")
dfCNRM$hyf <- paste("hy",dfCNRM$hy, sep = "")
dfCCSM$hyf <- paste("hy",dfCCSM$hy, sep = "")

# ori position of name fixer function block

nameFixer(dfGISS)
nameFixer(dfPCM)
nameFixer(dfMiro)
nameFixer(dfCNRM)
nameFixer(dfCCSM)

group_by(dfGISS, hy) -> dfGISSg
group_by(dfPCM,  hy) -> dfPCMg
group_by(dfMiro, hy) -> dfMirog
group_by(dfCCSM, hy) -> dfCCSMg
group_by(dfCNRM, hy) -> dfCNRMg

tblTmnSlopes <- read.csv("E:/tblTmnSlopes.txt")
areas <- cbind(tblTmnSlopes$SHCID, tblTmnSlopes$Area_m2)
areas3 <- areas
areas3[2:15, ] <- areas[1:14,]
areas3[1,] <- areas[15,]
areas3
dfAreas <- tbl_df(areas3)
names(dfAreas) <- c("SID", "Area_m2")
dfAreas[16,2] <- sum(dfAreas[,2]) 
dfAreas[16,1] <- 9999.
vAreas <- as.vector(dfAreas[,2])

dfAccPPT_GISS <- makeMeans_mm_to_m(dfGISS)
dfAccPPT_CCSM <- makeMeans_mm_to_m(dfCCSM)
dfAccPPT_Miro <- makeMeans_mm_to_m(dfMiro)
dfAccPPT_PCM  <- makeMeans_mm_to_m(dfPCM)
dfAccPPT_CNRM <- makeMeans_mm_to_m(dfCNRM)
```

## Including Plots

You can also embed plots, for example:

```{r}
dfRWC <- grabSID(1003)
dfRWCl <- melt(dfRWC, id="Date")

rwcTQ <- read.csv("X:/_05_KlamClime/07_inputTabular/USGS_Gage/RWC_tQ.csv")
dfRWCobs <- tbl_df(rwcTQ)

g <- ggplot(data = dfRWCl, aes(x = Date, y = value), color = variable)

ggplot(data = dfRWCl, aes(x = Date, y = value, color = variable)) +
        geom_line() + coord_cartesian(xlim = c(dfRWC$Date[900],dfRWC$Date[924])) +
        ggtitle("Redwood Creek Total Monthly Volume of Precip") +
        ylab("Precipitation/Month (m3/mo)")

#       #       #
#    Historic Data
#       #       #
Phase1Huc10_Historic_Ppt <- read.csv("X:/_05_KlamClime/07_inputTabular/Huc10/Hist/Phase1Huc10_Historic_Ppt.csv")
dfHistPpt <- tbl_df(Phase1Huc10_Historic_Ppt)
dfHistPpt$Date <- as.Date(dfHistPpt$TIMESTEP)

makeMeans_mm_to_m(dfHistPpt) -> dfAccPPT_Hist

dfRWCtq <- tbl_df(rwcTQ)
dfRWCtq$Datef <- dfRWCtq$Date

dfRWCtq$Date <- as.Date(dfRWCtq$Datef, "%m/%d/%Y")

#g <- ggplot(dfm1, aes(y = dfm1$`dfRWC_Model_Obs$Q_cfs`, x = dfm1$`dfRWC_Model_Obs$HistpptV`))
#g + geom_point() + geom_smooth(method = "lm", se = FALSE)


dfHistPpt$Date <- as.Date(dfHistPpt$TIMESTEP)
makeMeans_mm_to_m(dfHistPpt) -> dfAccPPT_Hist
grabSIDHist(dfAccPPT_Hist) -> dfAccPPT_Hist_RWC


inner_join(dfAccPPT_Hist_RWC, dfRWCtq, by = "Date") -> dfRWC_Model_Obs
dfRWC_Model_Obs$PptV <- dfRWC_Model_Obs$HistpptV
m1 <- lm(Q_cfs~PptV  ,data = dfRWC_Model_Obs)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

##  Streamflow Values for Redwood Creek

```{r}
RWC_11482500_DailyQ_cln <- read.delim("X:/_05_KlamClime/07_inputTabular/USGS_Gage/RWC_11482500_DailyQ_cln.txt")

dfRWCq <- tbl_df(RWC_11482500_DailyQ_cln)
dfRWCq$Date <- as.Date(dfRWCq$datetime, "%Y-%m-%d")

quants <- 0:100/100
quantile(dfRWCq$Q_cfs, quants,na.rm = TRUE) -> dfRWCQuants
tbl_df(dfRWCQuants) -> dfRWCQuants

names(dfRWCQuants) <- "Q_cfs"
dfRWCQuants$percentile <- quants

library(hydroTSM)



getQuant <- function(inputVal, dfQuants=dfRWCQuants){
        for(i in 1:100){
                logicTest <- (dfQuants$Q_cfs[i] > inputVal)
                #print(logicTest)
                if(logicTest){
                        returnVal <- dfQuants$percentile[i-1]
                        return(returnVal)
                }
        }
}


fdc(dfRWCq$Q_cfs, main="FDC for RWC, Historical") -> fdcRWC


```        



